|

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.Rmd
trying to get better line size for x dist power comparison

```{r different-x-dist-poly-power, fig.height = 3, fig.width = 5, fig.cap = "Power of conventional tests and visual tests on lineups produced by the non-linearity model under different distributions of regressor."}

dat_different_dist <- poly_conv_sim %>% 
  mutate(log_effect_size = log(effect_size)) %>%
  select(x_dist, log_effect_size, RESET4_p_value) %>%
  rename(RESET_p_value = RESET4_p_value) %>%
  pivot_longer(RESET_p_value) %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", 
                                       "Discrete", 
                                       stringr::str_to_title(x_dist))) %>%
  mutate(name = gsub("_p_value", " test", name)) %>%
  mutate(reject = value < 0.05) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", 
                         "Discrete", 
                         stringr::str_to_title(x_dist))) %>%
  mutate(conv_or_not = "Visual"))

>>>>

```{r different-x-dist-poly-power, fig.height = 3, fig.width = 7, fig.cap = "Power of conventional tests and visual tests on lineups produced by the non-linearity model under different fitted value distributions."}

dat_different_dist <- poly_conv_sim %>% 
  mutate(log_effect_size = log(effect_size)) %>%
  select(x_dist, log_effect_size, RESET4_p_value) %>%
  rename(RESET_p_value = RESET4_p_value) %>%
  pivot_longer(RESET_p_value) %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", 
                                       "Discrete", 
                                       stringr::str_to_title(x_dist))) %>%
  mutate(name = gsub("_p_value", " test", name)) %>%
  mutate(reject = value < 0.05) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", 
                         "Discrete", 
                         stringr::str_to_title(x_dist))) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(x_dist = factor(x_dist, 
      levels = c("Uniform", "Normal", 
                 "Lognormal", "Discrete")))

ggplot() +
  geom_smooth(data=filter(dat_different_dist, 
                          x_dist == "Uniform"),
              aes(log_effect_size, 
                  reject), 
                  col = "grey", 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, size=3) +
  geom_smooth(data=dat_different_dist,
              aes(log_effect_size, 
                  reject, 
                  col = x_dist), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, size=1) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(4,1,3,2)]) +
  scale_size_manual(values = c(1, 2, 3, 4)) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", linetype = "Test") +
  facet_wrap(~conv_or_not) +
  theme(legend.position="bottom")
```
